---
title: 'Lab 7: Multiple Linear Regression Intro'
author: "Devin Ngo"
date: "11/9/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, results = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, results = FALSE, warnings = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## explore penguins dataset 

Use `GGally:ggpairs()` to create a pairs plot 
```{r}
ggpairs(penguins)
```
That's kind of overkill. Let's simplify the variables that we include in our ggpairs plot:

- species 
- bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm, bill_depth_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```

## Multiple linear regression 

We are going to try to understand (a bit better) the relationships between mulitple predictor variables and an outcome variable which is penguin body mass. 

The different predictor variables we're going to try are:

- species 
- flipper length 
- sex
- bill depth 

### Model 1

Model body mass based on only flipper length and bill depth (bad idea... there are important variables missing)

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# Call model by name to return only coefficients
model_1

# More information on the coefficients and model"
summary(model_1)
```

If everything else is held constant, we expect for each one mm increase in flipper length, penguin  body mass is expected to increase by 51.54 g, on average. 

76% of variants in penguin body mass is explained by this model (penguin flipper length and bill depth). 

Actually - - we think that a model for penguin body mass should contain variables species, flipper length, and penguin sex 

```{r}
model_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

model_2

# flipper length, Gentoo, and male

# On average, given everything is a constant we expect a Gentoo penguin to be 836.26 larger in body mass than adelie on average. 

# On average, given everything is a constant we expect a male penguin to be 530.38 larger in body mass than female on average. 
```

## Visualize this model 

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~sex)
```

## A couple ways to get and report MLR model outcomes 

Use broom::tidy() to get model coefficient info in a tidy data frame.

```{r}
penguin_model2_coef <- tidy(model_2)

penguin_model2_coef
```


Try to write inline code `r` that spits out the coefficient for Gentoo 

`r penguin_model2_coef$estimate[4]` 

# Look at model diagnostics 

```{r}
plot(model_2)

summary(model_2)
```

## Report the model outputs in a summary table 

Use modelsummary:
```{r}
modelsummary(model_2)
```

Use stargazer:
```{r, results = "asis"}
stargazer(model_2, type = "html")
```



